---
output: github_document
---

# Programming Assignment 1

## Objects

```{r, objects}

dur_hablo_stressed <- 0.299
dur_hablo_unstressed <- 0.251
dur_o_stressed <- 0.097
dur_o_unstressed <- 0.067
int_o_stressed <- 68.060
int_o_unstressed <- 63.992
f0_o_stressed <- 127.757
f0_o_unstressed <- 137.994

```

## Operations

```{r, operations}

dur_hablo_stressed - dur_hablo_unstressed

dur_o_stressed - dur_o_unstressed

int_o_stressed - int_o_unstressed

f0_o_stressed - f0_o_unstressed
```

## Summary

Overall, the measurements from the stressed "habló" are bigger than the measurements from the unstressed "hablo". Specifically, the word "habló" is longer than the word "hablo". Also, the duration of the stressed [o] in "habló" is longer than the unstressed [o] in "hablo". The intensity is also higher in the stressed [o] in "habló" compared to the unstressed [o] in "hablo". Interestingly, however, the pitch (F0) of the unstressed [o] in "hablo" is higher than the pitch of the stressed [o] in "habló". I am not sure if this is somenthing that is supposed to be expected or if it could be due to an error both in the recording process or in the marking of the midpoint in Praat.



